### 2022-01-07 paper/paper.tex
clarify nonconservative terms

\trixi is designed as a simulation framework and library of high-order methods for conservation laws
of the form
\begin{equation}
\label{eq:hcl}
  \partial_t u(t, x) + \sum_{j=1}^d \partial_{x_j} f^j(u) = s(t, x, u),
  \quad t \in (0, T), x \in \Omega,
\end{equation}
in $d \in \{1, 2, 3\}$ space dimensions. Here, the independent variables are
time $t$ and space coordinates $x \in \Omega \subset \mathbb{R}^d$. The conserved
quantities are denoted as $u$, \eg, mass, momentum, and energy for the compressible
Euler equations of an ideal gas.
The physical system is specified by the fluxes $f^j$ and the source term $s$.
In addition, suitable initial and boundary conditions (ICs, BCs) are required.
\trixi also handles non-conservative PDE terms as in the shallow water equations or magnetohydrodynamics equations
with divergence cleaning.

>>>>

\trixi is designed as a simulation framework and library of high-order methods for conservation laws
of the form
\begin{equation}
\label{eq:hcl}
  \partial_t u(t, x) + \sum_{j=1}^d \partial_{x_j} f^j(u) = s(t, x, u),
  \quad t \in (0, T), x \in \Omega,
\end{equation}
in $d \in \{1, 2, 3\}$ space dimensions. Here, the independent variables are
time $t$ and space coordinates $x \in \Omega \subset \mathbb{R}^d$. The conserved
quantities are denoted as $u$, \eg, mass, momentum, and energy for the compressible
Euler equations of an ideal gas.
The physical system is specified by the fluxes $f^j$ and the source term $s$.
In addition, suitable initial and boundary conditions (ICs, BCs) are required.
\trixi also handles non-conservative PDE terms as in the shallow water equations
or magnetohydrodynamics equations with divergence cleaning, where source terms
can depend on derivatives of~$u$.
